### 2017-05-29 doc/categories.tex
Git more messing with section 5.
Missing file.

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.5]{omissionex.pdf}
  \caption{Omission scores for an example sentence for {\sc
      LM} and the two pathways, {\sc Textual} and {\sc Visual}, of
    {\sc Imaginet.}}
  \label{fig:omissionex}
\end{figure*}

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.25]{85826.jpg}
  \includegraphics[scale=0.25]{60596.jpg}
  \caption{Images retrieved for an example sentence (left) and the version of
    it with the  second word omitted (right).}
  \label{fig:omissionexpic}
\end{figure*}

@@

%\subsection{Salience of categories of words}
%\label{sec:salience}
In this section we propose novel techniques for interpreting the
activation patterns of neural networks trained on language tasks
from a linguistic point of view and focus
on the high level understanding of what types of words the networks
pay most attention to. Furthermore, we investigate if the networks
learn to assign appropriate amounts of importance to tokens depending
on their position and grammatical function in the sentences.\label{edit:whyposdep}
In Section \ref{sec:computeomission} we introduce \emph{omission scores};
a metric to measure the contribution of each token to the prediction of the networks.
Section \ref{sec:omitimaginet} aggregates the omission scores in terms
of dependency relations and part-of-speech categories and compares {\sc Visual}
and {\sc Textual}. Lastly Section \ref{sec:beyondlexical} investigates the extent to which
the importance of words for the different pathways depend on the words themselves,
their position and their grammatical function in the sentences.
% MAYBE THIS WOULD BE TOO MUCH
%We apply the proposed methods to explore
%the representations of {\sc Imaginet}, but also discuss how to generalize
%them to other architectures.

>>>>

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.3]{omissionex.pdf}
  \caption{Omission scores for an example sentence for {\sc LM} and
    the two pathways, {\sc Textual} and {\sc Visual}, of {\sc
      Imaginet.}}
  \label{fig:omissionex}
\end{figure*}

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.25]{85826.jpg}
  \includegraphics[scale=0.25]{60596.jpg}
  \caption{Images retrieved for the example sentence {\it a baby sits
      on a bed laughing with a laptop computer open} (left) and the
    same sentence with the second word omitted (right).}
  \label{fig:omissionexpic}
\end{figure*}

@@

%\subsection{Salience of categories of words}
%\label{sec:salience}
In this section we propose novel techniques for interpreting the
activation patterns of neural networks trained on language tasks
from a linguistic point of view and focus
on the high level understanding of what parts of input sentence the networks
pay most attention to. Furthermore, we investigate if the networks
learn to assign differential amounts of importance to tokens depending
on their position and grammatical function in the sentences.\label{edit:whyposdep}
In Section \ref{sec:computeomission} we introduce \emph{omission scores};
a metric to measure the contribution of each token to the prediction of the networks.
Section \ref{sec:omitimaginet} aggregates the omission scores in terms
of dependency relations and part-of-speech categories and compares {\sc Visual}
and {\sc Textual}. Section \ref{sec:beyondlexical} investigates the extent to which
the importance of words for the different networks depend on the words themselves,
their position and their grammatical function in the sentences.
% MAYBE THIS WOULD BE TOO MUCH
%We apply the proposed methods to explore
%the representations of {\sc Imaginet}, but also discuss how to generalize
%them to other architectures.
